Cerebral malaria follow-up visit data

### 2021-08-20 cm_follow_up_figures.Rmd
finalized figure 5 with updated follow-up analysis

  dplyr::filter(grepl("avg_Hb", variable)) %>% 
  mutate(measurement = ifelse(grepl("conc", variable), "THC", "O2_sat")) %>% 
  mutate(measurement = factor(measurement, levels = c("O2_sat", "THC"))) %>% 
  mutate(pvals = ifelse(measurement == "THC", round(thc_fu_pval, 3), round(o2sat_fu_pval, 3))) %>%

@@

  geom_segment(aes(x = 1, y = 1.4, xend = 2, yend = 1.4), size = 0.3) +
  geom_segment(aes(x = 1, y = 1.4, xend = 1, yend = 1.35), size = 0.3) +
  geom_segment(aes(x = 2, y = 1.4, xend = 2, yend = 1.35), size = 0.3) +
  geom_text(x = 1.5, y = 1.43, aes(label = paste0("p = ", pvals))) +

@@

@@

  dplyr::filter(!grepl("avg|second", variable)) %>% 
  mutate(measurement = ifelse(grepl("conc", variable), "THC", "O2_sat")) %>% 
  mutate(measurement = factor(measurement, levels = c("O2_sat", "THC"))) %>% 
  mutate(pvals = ifelse(measurement == "THC", round(thc_alpha_fu_pval, 3), round(o2sat_alpha_fu_pval, 3))) %>%

@@

  geom_segment(aes(x = 1, y = 1.4, xend = 2, yend = 1.4), size = 0.3) +
  geom_segment(aes(x = 1, y = 1.4, xend = 1, yend = 1.35), size = 0.3) +
  geom_segment(aes(x = 2, y = 1.4, xend = 2, yend = 1.35), size = 0.3) +
  geom_text(x = 1.5, y = 1.43, aes(label = paste0("p = ", pvals))) +

>>>>

  dplyr::filter(grepl("avg_Hb", variable)) %>% 
  mutate(measurement = ifelse(grepl("conc", variable), "THC", "O2_sat")) %>% 
  mutate(measurement = factor(measurement, levels = c("O2_sat", "THC"))) %>% 
  mutate(pvals = ifelse(measurement == "THC", round(thc_fu_pval, 3), round(o2sat_fu_pval, 3))) %>% 
  mutate(ycoord = ifelse(measurement == "THC", 400, 100)) %>%

@@

  geom_segment(aes(x = 1, y = ycoord, xend = 2, yend = ycoord), size = 0.3) +
  geom_segment(aes(x = 1, y = ycoord, xend = 1, yend = ycoord - .04*ycoord), size = 0.3) +
  geom_segment(aes(x = 2, y = ycoord, xend = 2, yend = ycoord - .04*ycoord), size = 0.3) +
  geom_text(x = 1.5, aes(y = ycoord + .025*ycoord, label = paste0("p = ", pvals))) +

@@

library(scales)

@@

  dplyr::filter(!grepl("avg|second", variable)) %>% 
  mutate(measurement = ifelse(grepl("conc", variable), "THC", "O2_sat")) %>% 
  mutate(measurement = factor(measurement, levels = c("O2_sat", "THC"))) %>% 
  mutate(pvals = ifelse(measurement == "THC", scientific(thc_alpha_fu_pval, 3), scientific(o2sat_alpha_fu_pval, 3))) %>%

@@

  geom_segment(aes(x = 1, y = 1.4, xend = 2, yend = 1.4), size = 0.3) +
  geom_segment(aes(x = 1, y = 1.4, xend = 1, yend = 1.35), size = 0.3) +
  geom_segment(aes(x = 2, y = 1.4, xend = 2, yend = 1.35), size = 0.3) +
  geom_text(x = 1.5, y = 1.43, aes(label = paste0("p < .0001"))) +
